Stat 400 Project

### 2021-12-13 Stat 400 proj.Rmd
Added prop_vac to bootstrap and removed some random extra lines

      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance & vac_eff == F){
        newly_infected <- c(newly_infected, j)
      }

    }
  }

@@

set.seed(400)
n=50
y <- simulator(n,100,10,10,2,1,.95)
x <- 0:n

plot <- ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

@@

get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc'){
  #Create data frame to store samples
  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
  samps <- data.frame(samps)

@@

  for(i in 1:sample_size){
    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist)
  }

@@

plot_dat <- get_bootstrap_cis(days=50, num_subjects=3500, x_dim=100, y_dim=100, I_0=18, inf_dist=0.5, sample_size=20)

@@

daily_cases <- y
boot.case <- boot(daily_cases, mean_func, 2000)

plot(boot.case)

boot.ci(boot.case, conf = .95, type = c("perc", "basic", "norm", "bca"))

>>>>

      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance & (vac_eff == F)){
        newly_infected <- c(newly_infected, j)
      }
    }
  }

@@

set.seed(400)
n=50
y <- simulator(100, 1000, 1, 1, 5, 0.005, 0)
x <- 0:100

ggplot() +
  geom_line(aes(x=x, y=y)) +
  xlab('Day') +
  ylab('Number of Cases') +
  ggtitle('Number of Covid-19 cases over time')

@@

get_bootstrap_cis <- function(days, num_subjects, x_dim, y_dim, I_0, inf_dist, sample_size, ci_type='perc', prop_vac = 0){
  #Create data frame to store samples
  samps <- matrix(data=NA, nrow=sample_size, ncol=days + 1)
  samps <- data.frame(samps)

@@

  for(i in 1:sample_size){
    samps[i, ] <- simulator(days, num_subjects, x_dim, y_dim, I_0, inf_dist, prop_vac)
  }

@@

plot_dat <- get_bootstrap_cis(days=50, num_subjects=100, x_dim=1, y_dim=1, I_0=5, inf_dist=0.5, sample_size=20, prop_vac = 0.8)

@@
